%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Course Objectives}
\begin{itemize}[<+->]
\item Introduction to statistics
  \begin{itemize}
  \item Experiment design
  \item Probability
  \item Distributions of random variables
  \item Statistical tests
  \item Regression models
  \end{itemize}
\item Introduction to R
  \begin{itemize}
  \item Basics of the language
  \item Notebook-like usage
  \item Manipulating and viewing data
  \item External tools (e.g. Markdown, \LaTeX, Github)
  \end{itemize}
\end{itemize}
\end{frame}


\begin{frame}
  \frametitle{Why I Like This Class}
  \begin{itemize}[<+->]
  \item Statistics basics are good to refresh
    \begin{itemize}
    \item There are subtle nuances
    \item It's very useful/relevant to many fields
    \item Statistics is one perspective on how to find the truth, a
      formalization of the scientific method
    \end{itemize}
  \item R is a fun programming language
    \begin{itemize}
      \item We'll be using it for specific purposes (statistics) so
        you only need to learn the relevant parts.
      \item RStudio helps a lot in learning R
      \item One tricky part: base R vs. Tidyverse
    \end{itemize}
  \item Online classes are relatively new and have a lot of promise
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Approach: Leverage Book, Instructor, and Class}

  {\bf The book} gives a good overview of statistics, many examples, and
  problem sets.

  \pause

  {\bf The professor} will help interpret the book, create R
  tutorials, and connect the material to other classes, history, and
  professional experience in programming, data science, and machine
  learning.

  \pause

  {\bf The students} will contribute to the class by asking questions,
  discussing, sharing relevant experience, and by doing a final project.
  
\end{frame}


\begin{frame}
  \frametitle{Policies and Schedule}
  See syllabus and Canvas.
\end{frame}

\begin{frame}
  \frametitle{Introductions}
  \begin{itemize}
  \item What is your name (including any nicknames or pronunciation help)?
  \item What program are you in?
  \item Any experience with R or stats?
  \item Places: where you were born, where you grew up, where you currently live, and one place you'd like to visit?
  \end{itemize}
\end{frame}
